### 2023-03-13 main/chapter_theory.tex
comma neutrinos

% made using:
% https://www.tablesgenerator.com/latex_tables
\begin{table}[tp]
\centering
\begin{tabular}{cc}
fermions                                        & mass limit$\,\eV[G]$ \\[0.2em]
$\neutralino_1$ (stable)                        & $> 46$         \\
$\neutralino_1$ (unstable)                      & $> 380$        \\
$\neutralino_2$,$\neutralino_3$,$\neutralino_4$ & $> 750$        \\
$\chargino_1$,$\chargino_2$                     & $> 94$         \\[1em]
bosons                                          & mass limit$\,\eV[G]$ \\[0.2em]
$\tilde \nu$                                    & $> 94$         \\
$\tilde e$                                      & $> 107$        \\
$\tilde \mu$                                    & $> 94$         \\
$\tilde \tau$                                   & $> 81.9$       \\
$\tilde q$                                      & $> 1220$       \\
$\tilde b$                                      & $> 1270$       \\
$\tilde t$                                      & $> 1310$       \\
$\tilde g$                                      & $> 2300$
\end{tabular}
\caption[%
Mass limits for particles of the Minimal Supersymmetric Standard Model%
]{%
Mass limits for particles of the Minimal Supersymmetric Standard Model as
reported under by the Particle Data Group under loose
assumptions, quoted at ``$\mathrm{CL}=95.0\%$''~\cite{pdg2022ynf}.
The charges of these particles equal the charges of their Standard Model
partners, which are listed in
Table~\ref{tab:theory_particles_sm_properties}.
\\[0.4em]
All of these limits assume R-parity conservation and various other,
instance-specific constraints.
For example, the limit of
$m(\neutralino_2,\neutralino_3,\neutralino_4) > 750\,\eV[G]$
assumes that $m(\neutralino_1) < 100\,\eV[G]$.
Many stronger constraints are reported within the constraints of simplified
models.
Limits on R-parity violating models differ, and can be either stronger or
weaker.
In the stable $\neutralino_1$ case, the $\neutralino_1$ is the lightest
supersymmetric particle and a dark matter candidate;
in the unstable $\neutralino_1$ case, it rapidly decays.
Stronger limits can be set for particles that live long enough to decay within
the sensitive materials of collider detectors.
\\[0.4em]
All listed bosons are spin-$0$ and all listed fermions are spin-$1/2$.
}
\label{tab:theory_particles_mssm_mass_limits}
\end{table}

>>>>

% made using:
% https://www.tablesgenerator.com/latex_tables
\begin{table}[tp]
\centering
\begin{tabular}{cc}
fermions                                        & mass limit$\,\eV[G]$ \\[0.2em]
$\neutralino_1$ (stable)                        & $> 46$         \\
$\neutralino_1$ (unstable)                      & $> 380$        \\
$\neutralino_2$,$\neutralino_3$,$\neutralino_4$ & $> 750$        \\
$\chargino_1$,$\chargino_2$                     & $> 94$         \\[1em]
bosons                                          & mass limit$\,\eV[G]$ \\[0.2em]
$\tilde \nu_e$,$\tilde \nu_\mu$,$\tilde \nu_\tau$ & $> 94$         \\
$\tilde e$                                      & $> 107$        \\
$\tilde \mu$                                    & $> 94$         \\
$\tilde \tau$                                   & $> 81.9$       \\
$\tilde q$                                      & $> 1220$       \\
$\tilde b$                                      & $> 1270$       \\
$\tilde t$                                      & $> 1310$       \\
$\tilde g$                                      & $> 2300$
\end{tabular}
\caption[%
Mass limits for particles of the Minimal Supersymmetric Standard Model%
]{%
Mass limits for particles of the Minimal Supersymmetric Standard Model as
reported under by the Particle Data Group under loose
assumptions, quoted at ``$\mathrm{CL}=95.0\%$''~\cite{pdg2022ynf}.
The charges of these particles equal the charges of their Standard Model
partners, which are listed in
Table~\ref{tab:theory_particles_sm_properties}.
\\[0.4em]
All of these limits assume R-parity conservation and various other,
instance-specific constraints.
For example, the limit of
$m(\neutralino_2,\neutralino_3,\neutralino_4) > 750\,\eV[G]$
assumes that $m(\neutralino_1) < 100\,\eV[G]$.
Many stronger constraints are reported within the constraints of simplified
models.
Limits on R-parity violating models differ, and can be either stronger or
weaker.
In the stable $\neutralino_1$ case, the $\neutralino_1$ is the lightest
supersymmetric particle and a dark matter candidate;
in the unstable $\neutralino_1$ case, it rapidly decays.
Stronger limits can be set for particles that live long enough to decay within
the sensitive materials of collider detectors.
\\[0.4em]
All listed bosons are spin-$0$ and all listed fermions are spin-$1/2$.
}
\label{tab:theory_particles_mssm_mass_limits}
\end{table}
